|

### 2024-08-09 doc/paper.qmd
do_analysis.py code

**EM**: Earnings Management  
**IDE**: Integrated Development Environment  
**UK**: United Kingdom  
**US**: United States  
**WRDS**: Wharton Research Data Services

@@

### Smoothing Reported Operating Earnings Using Accruals (EM1)
`EM1` is a measure that assesses how much insiders (e.g., company executives) smooth or stabilize reported earnings by manipulating accruals. The underlying idea is that firms may attempt to reduce fluctuations in their reported operating income to present a more stable financial performance to investors. This measure indicates the degree to which insiders exercise accounting discretion to smooth reported earnings, with lower values of EM1 suggesting more aggressive earnings smoothing.

To calculate this measure:
1.	Accruals are computed using changes in various components of a firm’s balance sheet and income statement, such as total current assets, cash, current liabilities, short-term debt, taxes payable, and depreciation.
$$
\text{Accruals}_{it} = (\Delta \text{CA}_{it} - \Delta \text{Cash}_{it}) - (\Delta \text{CL}_{it} - \Delta \text{STD}_{it} - \Delta \text{TP}_{it}) - \text{Dep}_{it}
$$

$$
\begin{aligned}
where:  \\
\Delta \text{CA}_{it} & = \text{Change in total current assets} \\
\Delta \text{Cash}_{it} & = \text{Change in cash and cash equivalents} \\
\Delta \text{CL}_{it} & = \text{Change in total current liabilities} \\
\Delta \text{STD}_{it} & = \text{Change in short-term debt included in current liabilities} \\
\Delta \text{TP}_{it} & = \text{Change in income taxes payable} \\
\text{Dep}_{it} & = \text{Depreciation and amortization expense}
\end{aligned}
$$

2.	The operating cash flow is indirectly derived from operating income minus accruals
$$
\text{CFO}_{it} = \text{Operating Income}_{it} - \text{Accruals}_{it}
$$

3.	EM1 is then calculated as the country’s median ratio of the firm-level standard deviations of operating income and operating cash flow. Both these standard deviations are scaled by lagged total assets to control for differences in firm size.
$$
\text{EM1} = \text{Median}\left(\frac{\sigma(\text{Operating Income}_{it})}{\sigma(\text{Operating Cash Flow}_{it})}\right) \quad \text{scaled by lagged total assets}
$$

>>>>

**CFO**: Operating Cash Flow  
**EM**: Earnings Management  
**IDE**: Integrated Development Environment  
**UK**: United Kingdom  
**US**: United States  
**WRDS**: Wharton Research Data Services

@@

### Smoothing Reported Operating Earnings Using Accruals (EM1)
`EM1` is a measure that assesses how much insiders (e.g., company executives) smooth or stabilize reported earnings by manipulating accruals. The concept is that firms may attempt to reduce fluctuations in their reported operating income to present a more stable financial performance to investors. This measure reflects the degree to which insiders use accounting discretion to smooth reported earnings, with lower values of EM1 suggesting more aggressive earnings smoothing.

To calculate this measure:
1.	Compute Accruals by using changes in various components of a firm’s balance sheet and income statement, such as total current assets, cash, current liabilities, short-term debt, taxes payable, and depreciation:

$$
\begin{aligned}
\text{Accruals}_{it} &= (\Delta \text{CA}_{it} - \Delta \text{Cash}_{it}) - (\Delta \text{CL}_{it} - \Delta \text{STD}_{it} - \Delta \text{TP}_{it}) - \text{Dep}_{it} 
& \\
\text{where:} \\
\Delta \text{CA}_{it} & = \text{Change in total current assets} \\
\Delta \text{Cash}_{it} & = \text{Change in cash and cash equivalents} \\
\Delta \text{CL}_{it} & = \text{Change in total current liabilities} \\
\Delta \text{STD}_{it} & = \text{Change in short-term debt included in current liabilities} \\
\Delta \text{TP}_{it} & = \text{Change in income taxes payable} \\
\text{Dep}_{it} & = \text{Depreciation and amortization expense}
\end{aligned}
$$

2.	Derive Operating Cash Flow (CFO) that is indirectly derived from operating income minus accruals:

$$
\text{CFO}{it} = \text{Operating Income}_{it} - \text{Accruals}_{it}
$$

3.	Calculate EM1, which is determined as the country’s median ratio of the firm-level standard deviations of operating income and operating cash flow. Both standard deviations are scaled by lagged total assets to control for differences in firm size:
$$
\text{EM1} = \text{Median}\left(\frac{\sigma(\text{Operating Income}_{it})}{\sigma(\text{Operating Cash Flow}_{it})}\right) \quad \text{scaled by lagged total assets}
$$
